Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
edits

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis 
  from a transfer function representation into a state-space representation. 
  Such representation allows to study the  input-to-state dynamics, while 
  transfer functions represents only input-output relations and cannot be 
  enough to ensure deeper properties, e.g., the safety property.
%
\item We proposes a synthesis of state-feedback controllers that ensures 
  safety properties, that is only  possible in state-space representation. 
  In addition to the already existing stability conditions which is a much 
  harder problem.
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase 
  speed whilst retaining soundness. Both approaches provide sound
  synthesis of state-feedback systems considering the various
  error sources in the implementation of the control algorithm and in the
  computational modeling of plant dynamics.
%
\item We develop a model for different sources quantization and their
  effect on the state-space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}

@@

Program synthesizers are an ideal fit for synthesis of %parametric
digital controllers, since the semantics of programs capture effects such as
FWL precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use
CEGIS for the synthesis of switching controllers for stabilizing
continuous-time plants with polynomial dynamics.  The work extends to affine
systems, finding a major challenge in the hardness of solving linear
arithmetic with the state-of-the-art SMT solvers.  Since this approach uses
switching models instead of linear dynamics for the digital controller, it
entirely circumvents the FWL problem, but potentially incurs state-space
explosion issues.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the
same authors use a CEGIS-based approach for synthesizing continuous-time
switching controllers that guarantee \emph{reach-while-stay} properties of
closed-loop systems, i.e., properties that specify a set of goal states and
safe states (constrained reachability).  This solution is based on
synthesizing control Lyapunov functions for switched systems, that yield
switching controllers with a guaranteed minimum dwell time in each mode. 
However, both approaches are not suitable for the kind of control we seek to
synthesize.

The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the
synthesis of stabilizing controllers for continuous plants described as
transfer functions, by exploiting bit-accurate verification of
software-implemented digital controllers~\cite{IsmailBCFF15,Bessa16}.  While this work
also makes use of a CEGIS-based technique, the approach is restricted to
synthesizing digital controllers for stable closed-loop systems described
via transfer function models.  In contrast, in the current paper we consider
a state-space representation of the physical system, which is known to present
various advantages over transfer function representation \cite{Astrom08}: (i) 
easy to generalize for the multivariate systems (i.e., with multiple inputs 
and outputs); (ii) shows the state-to-input relationships offering an internal 
model of the system; and (iii) allows to synthesize control systems that ensures
properties about the internal dynamics, e.g., to synthesize controllers that make
the closed-loop system \emph{safe}. This work focuses on the \emph{safety} of 
internal states, such property is usually overlooked in the previous cited 
works, but plays an important role in real world systems, where systems states 
cannot assume any real value. Moreover, this work integrates an
abstraction/refinement step inside the main CEGIS loop.

The tool Pessoa~\cite{mazo2010pessoa} synthesizes
correct-by-design embedded control software, in a Matlab ToolBox.  It is based on the abstraction
of a physical system to an equivalent finite-state machine and on the
computation of reachability properties over the finite-state machine.  Based
on this safety specification over state values, Pessoa can synthesize
embedded controller software for a range of properties.
The embedded controller software can be more complicated than
the state-feedback control we synthesized, and the properties 
available cover more detail.
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the quantization error
introduced by Digital-to-Analogue/Analogue-to-Digital conversion needed for
synthesizing fixed-point digital controllers.

@@

The classical approach to control synthesis has often disregarded
quantization, thus resulting in general to unsound digital controllers. 
Modern techniques focus on different elements of discretization effects,
including delayed response~\cite{Duggirala2015}, and Finite Word Length
(FWL) semantics, with the goal either to verify (e.g.,~ \cite{daes20161}) or
to optimize (e.g.,~ \cite{oudjida2014design}) given implementations.

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A~more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analysis in~\cite{DBLP:conf/hybrid/RouxJG15,
DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
discrete system dynamics using Semi-Definite Programming (SDP).  While the
former uses bounded-input and bounded-output (BIBO) properties to determine stability, 
the latter uses Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
floating-point arithmetic and soundness is checked by bounding the error. 
An alternative approach is taken by~\cite{park2016scalable}, where the
verification of given control code is performed against a known model by
extracting an LTI model of the code through symbolic execution.  In order to
account for rounding errors, an upper bound is introduced in the
verification phase.  The work in \cite{picasso2003stabilization,
picasso2002construction} introduces attractive invariant sets as a mechanism
to bound the quantization error effect on stabilization as an invariant set
that always converges toward the controllable set.  In a similar fashion,
\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
and bounds its trajectory to a known region over a finite period of time. 
This technique works for both linear and non-linear systems.

@@

We consider models of physical plants expressed as ordinary differential equations (ODEs), 
which we assume to be controllable and under full state information (namely where we have access to all the model variables):  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
\end{align}
where $t \in \mathbb R_0^+$, 
where $A$ and $B$ are matrices that fully specify the continuous plant, 
and with initial states set as $x(0)$. 
Whilst we ideally would like to work on the continuous-time plant, 
in this work Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in the Appendix~\ref{sec:appendix:LTIbackground}) into %\textcolor{red}{What is subscript ``d''?}
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k. 
\end{align} 
where $k \in \mathbb N$, 
and with initial state $x_{0}=x(0)$. $A_d$ and $B_d$ denote the matrices that describes the discretized plant dynamics and $A$ and $B$ the continuous plant dynamics. 
Later, we will deal with the issue of variable quantization, as introduced by the ADC/DAC conversion blocks.

@@

In this study, we are not limited to the synthesis of digital stabilizing
controllers -- a well known task in the literature on digital control system
-- but target safety requirements with an overall approach that is sound and
automated.  More specifically, we require that the closed-loop system
\eqref{eq:closedloopss} meets given safety specifications.  A safety
specification raises a requirement on the states of the model, such that the
feedback controller (namely the choice of the gains matrix $K$) must ensure that
the states never exit such requirement.  Note that a stable, closed-loop
system is not necessarily a safe system: indeed, the state values may leave
the safe space whilst they converge to the equilibrium, which is typical in
the case of oscillatory dynamics.  However, a safe system will always be
stable.  In~this work, the safety property represented by $\phi_{safety}$ is
encoded as follows:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
%
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
instant, respectively.  This means that the states will always be within the
$n$-dimensional hyper-box.

Furthermore, it is practically relevant to consider the 
constraints $\phi_{init}$ on the input
signal $u_{k}$ and $\phi_{input}$ on the initial states $x_0$,
which we assume have given bounds:
$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
$\phi_{input} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
In the first case, this means that the control input saturates in view of
physical constraints.

@@

\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}. We consider the error introduced by the DAC to be equal to zero, since the domain of the plant is at a higher precision than the controller.
%More details on how to model quantization as noise are given in the 
%Appendix~\ref{appendix:quantization-noise}.
\item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints. Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
$$(\phi_{init} \wedge \phi_{input} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$

\end{enumerate}
\item In the {\sc synthesize} phase, we synthesize a candidate controller
%We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
% specification defined by Jury's 
%criteria. %, and try to synthesise a controller that meets these specs.
% For a stabilized closed-loop, which is necessary for our safety property, we need
% these roots to remain within the unit circle, which we verify using Jury's criteria.
% Notice that in our polynomials $c_0=1$ and we only use reals.
% Once we have established convergence, we may examine the 
% safety specification $\phi_{safety}$.
  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
  $\phi_{stability} \wedge \phi_{safety} \wedge \phi_{init}^{K}$ by invoking a SAT solver.
%%   We obtain it by solving the SAT formula 
%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
%% that satisfies the input constraint and Jury's criteria for 
%% $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
%% where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
If there is no candidate solution we return UNSAT and exit the loop.
\item Once we have a candidate solution, we perform a safety verification % If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
  %
  of the 
  %consisting of evaluating the
  progression of the system from $\phi_{init}$ over time,
$x_{k+1} \models \phi_{safety}$. %% For this purpose we require 
%% an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
%% from which the system progresses.
% Obviously, this set $x_0$ 
% must satisfy the specification; otherwise, the system will be unsafe to begin with.
% We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
% The presence of $\mat{T}$ is because this will typically be given in the original 
% state-space.
%% Next, we use abstract acceleration to get a second abstraction that 
  %% encompasses the accelerated continuous reach-tube over an unbounded time.
  In order to compute the progression of point $x_0$ at iteration $k$,
  we accelerate the dynamics of the closed-loop system and obtain:
  %we take the
  %the closed-loop model:
  %$x_{k+1}=\mat{A}_{t}x_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)$
  %and accelerate it to:
%
\begin{align}
%\label{eq:acc_observer_LTI_cf}
x=&(A_d-B_dK)^kx_0
%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
+\sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3) : B_n= [1\ 1 \cdots \ 1 ]^T
\end{align}
As this still requires us to verify the system for every $k$ up to infinity, 
we use abstract acceleration again to obtain
the reach-tube, i.e., the set of all reachable states at all times given an initial set $\phi_{init}$:
\begin{align}
\label{eq:aa_observer_LTI_cf}
\hat{X}^\#
=&\mathcal{A} X_0 + \mathcal{B}_{n} N\\
X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber
\end{align}
%
where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are abstract matrices for the closed-loop system \cite{cattaruzza2015unbounded}, whereas the set N is non-deterministically chosen.

>>>>

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis 
  from a transfer function representation into a state-space representation. 
  Such representation allows to study the  input-to-state dynamics, while 
  transfer functions represents only input-output relations and cannot be 
  enough to ensure deeper properties, e.g., the safety property.
%
\item We proposes a synthesis of state-feedback controllers that guarantees 
  safety properties, that is only  possible in state-space representation. 
  In addition to the already existing stability conditions which is a much 
  harder problem.
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase 
  speed whilst retaining soundness. Both approaches provide sound
  synthesis of state-feedback systems considering the various
  error sources in the implementation of the control algorithm and in the
  computational modeling of plant dynamics.
%
\item We develop a model for different sources quantization and their
  effect on the state-space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}

@@

Program synthesizers are an ideal fit for synthesis of %parametric
digital controllers, since the semantics of programs capture effects such as
FWL precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use
CEGIS for the synthesis of switching controllers for stabilizing
continuous-time plants with polynomial dynamics.  The work extends to affine
systems, finding a major challenge in the hardness of solving linear
arithmetic with the state-of-the-art SMT solvers.  Since this approach uses
switching models instead of linear dynamics for the digital controller, it
entirely circumvents the FWL problem, but potentially incurs state-space
explosion issues.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the
same authors use a CEGIS-based approach for synthesizing continuous-time
switching controllers that guarantee \emph{reach-while-stay} properties of
closed-loop systems, i.e., properties that specify a set of goal states and
safe states (constrained reachability).  This solution is based on
synthesizing control Lyapunov functions for switched systems that yield
switching controllers with a guaranteed minimum dwell time in each mode. 
However, both approaches are not suitable for the kind of control we seek to
synthesize.

The work in~\cite{DBLP:journals/corr/AbateBCCDKK16} investigates the
synthesis of stabilizing controllers for continuous plants described as
transfer functions, by exploiting bit-accurate verification of
software-implemented digital controllers~\cite{IsmailBCFF15,Bessa16}.  While this work
also makes use of a CEGIS-based technique, the approach is restricted to
synthesizing digital controllers for stable closed-loop systems described
via transfer function models.  By contrast, in the current paper we consider
a state-space representation of the physical system, which is known to present
various advantages over transfer function representation \cite{Astrom08}:
(i)~easy to generalize for the multivariate systems (i.e., with multiple inputs 
and outputs); (ii)~shows the state-to-input relationships offering an internal 
model of the system; and (iii)~allows to synthesize control systems with
guarantees about the internal dynamics, e.g., to synthesize controllers that make
the closed-loop system \emph{safe}. This work focuses on the \emph{safety} of 
internal states, such property is usually overlooked in the previous cited 
works, but plays an important role in real world systems, where system
variables cannot assume arbitrary real values. Moreover, our work integrates an
abstraction/refinement step inside the main CEGIS loop.

The tool Pessoa~\cite{mazo2010pessoa} synthesizes
correct-by-design embedded control software, in a Matlab toolbox.  It is based on the abstraction
of a physical system to an equivalent finite-state machine and on the
computation of reachability properties over the finite-state machine.  Based
on this safety specification, Pessoa can synthesize
embedded controller software for a range of properties.
The embedded controller software can be more complicated than
the state-feedback control we synthesized, and the properties 
available cover more detail.
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the quantization error
introduced by Digital-to-Analogue/Analogue-to-Digital conversion needed for
synthesizing fixed-point digital controllers.

@@

The classical approach to control synthesis has often disregarded
quantization, thus resulting in general to unsound digital controllers. 
Modern techniques focus on different elements of discretization effects,
including delayed response~\cite{Duggirala2015}, and Finite Word Length
(FWL) semantics, with the goal either to verify (e.g.,~\cite{daes20161}) or
to optimize (e.g.,~\cite{oudjida2014design}) given implementations.

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A~more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analysis in~\cite{DBLP:conf/hybrid/RouxJG15,
DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
discrete system dynamics using Semi-Definite Programming (SDP).  While the
former uses bounded-input and bounded-output (BIBO) properties to determine stability, 
the latter uses Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
floating-point arithmetic and soundness is checked by bounding the error. 
An alternative approach is taken by~\cite{park2016scalable}, where the
verification of given control code is performed against a known model by
extracting an LTI model of the code through symbolic execution.  In order to
account for rounding errors, an upper bound is introduced in the
verification phase.  The work in \cite{picasso2003stabilization,
picasso2002construction} introduces attractive invariant sets as a mechanism
to bound the quantization error effect on stabilization as an invariant set
that always converges toward the controllable set.  In a similar fashion,
\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
and bounds its trajectory to a known region over a finite period of time. 
This technique works for both linear and non-linear systems.

@@

We consider models of physical plants expressed as ordinary differential equations (ODEs), 
which we assume to be controllable and under full state information (namely where we have access to all the model variables):  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
\end{align}
where $t \in \mathbb R_0^+$, 
where $A$ and $B$ are matrices that fully specify the continuous plant, 
and with initial states set as $x(0)$. 
Whilst we ideally would like to work on the continuous-time plant, 
in this work Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in Appendix~\ref{sec:appendix:LTIbackground}) into %\textcolor{red}{What is subscript ``d''?}
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k. 
\end{align} 
where $k \in \mathbb N$, 
and with initial state $x_{0}=x(0)$. $A_d$ and $B_d$ denote the matrices that describes the discretized plant dynamics and $A$ and $B$ the continuous plant dynamics. 
Later, we will deal with the issue of variable quantization, as introduced by the ADC/DAC conversion blocks.

@@

In this study, we are not limited to the synthesis of digital stabilizing
controllers -- a well known task in the literature on digital control system
-- but target safety requirements with an overall approach that is sound and
automated.  More specifically, we require that the closed-loop system
\eqref{eq:closedloopss} meets given safety specifications.  A safety
specification raises a requirement on the states of the model, such that the
feedback controller (namely the choice of the gains matrix $K$) must ensure that
the states never exit such requirement.  Note that a stable, closed-loop
system is not necessarily a safe system: indeed, the state values may leave
the safe space whilst they converge to the equilibrium, which is typical in
the case of oscillatory dynamics.  However, a safe system will always be
stable.  In~this work, the safety property represented by $\phi_\mathit{safety}$ is
encoded as follows:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_\mathit{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
%
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
instant, respectively.  This means that the states will always be within the
$n$-dimensional hyper-box.

Furthermore, it is practically relevant to consider the 
constraints $\phi_\mathit{init}$ on the input
signal $u_{k}$ and $\phi_\mathit{input}$ on the initial states $x_0$,
which we assume have given bounds:
$\phi_\mathit{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
$\phi_\mathit{input} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
In the first case, this means that the control input saturates in view of
physical constraints.

@@

\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}. We consider the error introduced by the DAC to be equal to zero, since the domain of the plant is at a higher precision than the controller.
%More details on how to model quantization as noise are given in the 
%Appendix~\ref{appendix:quantization-noise}.
\item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$, based on the input constraints. Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k) \Rightarrow \phi_\mathit{init}^{K}$$

\end{enumerate}
\item In the {\sc synthesize} phase, we synthesize a candidate controller
%We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
% specification defined by Jury's 
%criteria. %, and try to synthesise a controller that meets these specs.
% For a stabilized closed-loop, which is necessary for our safety property, we need
% these roots to remain within the unit circle, which we verify using Jury's criteria.
% Notice that in our polynomials $c_0=1$ and we only use reals.
% Once we have established convergence, we may examine the 
% safety specification $\phi_{safety}$.
  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
  $\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ by invoking a SAT solver.
%%   We obtain it by solving the SAT formula 
%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
%% that satisfies the input constraint and Jury's criteria for 
%% $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
%% where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
If there is no candidate solution we return UNSAT and exit the loop.
\item Once we have a candidate solution, we perform a safety verification % If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
  %
  of the 
  %consisting of evaluating the
  progression of the system from $\phi_\mathit{init}$ over time,
$x_{k+1} \models \phi_\mathit{safety}$. %% For this purpose we require 
%% an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
%% from which the system progresses.
% Obviously, this set $x_0$ 
% must satisfy the specification; otherwise, the system will be unsafe to begin with.
% We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
% The presence of $\mat{T}$ is because this will typically be given in the original 
% state-space.
%% Next, we use abstract acceleration to get a second abstraction that 
  %% encompasses the accelerated continuous reach-tube over an unbounded time.
  In order to compute the progression of point $x_0$ at iteration $k$,
  we accelerate the dynamics of the closed-loop system and obtain:
  %we take the
  %the closed-loop model:
  %$x_{k+1}=\mat{A}_{t}x_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)$
  %and accelerate it to:
%
\begin{align}
%\label{eq:acc_observer_LTI_cf}
x=&(A_d-B_dK)^kx_0
%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
+\sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3) : B_n= [1\ 1 \cdots \ 1 ]^T
\end{align}
As this still requires us to verify the system for every $k$ up to infinity, 
we use abstract acceleration again to obtain
the reach-tube, i.e., the set of all reachable states at all times given an initial set $\phi_\mathit{init}$:
\begin{align}
\label{eq:aa_observer_LTI_cf}
\hat{X}^\#
=&\mathcal{A} X_0 + \mathcal{B}_{n} N\\
X_0 =&\left \{x : x \models \phi_\mathit{init} \right\}\nonumber
\end{align}
%
where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are abstract matrices for the closed-loop system \cite{cattaruzza2015unbounded}, whereas the set N is non-deterministically chosen.
